Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-12 results.tex
Edited section 4.2
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1046 ccdd05d5-56c1-461a-bf98-85f6876523b4

We expect two known contributions to the \SNR\ loss to arise in our
implementation of the \lloid\ algorithm.  The first is the \SNR\ loss due to
the truncation of the \SVD\ basis and estimates for it
exist~\citep{Cannon:2010p10398}.  The second comes from non ideal
implementations of re-sampling that cause signal loss.  The \SNR\ loss is to be
compared with the mismatch of 0.03 that arises from the discreteness of the
template bank.  We will consider a target \SNR\ loss to be a factor of 10
smaller than this, i.e., no more than $\sim$0.003.

It is also within reason that some \SNR\ loss could arise from other
suboptimalities of implementation in our test pipeline.  To gauge
accurately how well the pipeline is performing we tested the response to a
unit impulse.  By taking the inner product of the impulse response for each channel
with the template, we can gauge very accurately the loss in
\SNR\ due to the approximations we have made and any inadequacies in
our implementation.

>>>>

The \SNR\ loss is to be compared with the mismatch of 0.03 that arises from the
discreteness of template bank designed for a minimum match of 0.97.  We will consider
an acceptable \SNR\ loss to be a factor of 10 smaller than this, that is, no more
than 0.003.

We expect two main contributions to the \SNR\ loss to arise in our
implementation of the \lloid\ algorithm.  The first is the \SNR\ loss due to
the truncation of the \SVD\ at $L^s < M$ basis templates.  As remarked upon in
section~\ref{sec:svd} and \citet{Cannon:2010p10398}, this effect is measured by
the \SVD\ tolerance.  The second comes from the limited bandwidth of the
interpolation filters used to match the sample rates of the partial \SNR\ streams.
\SNR\ loss could also arise if the series rather than parallel connection of the
decimation and interpolation filters reduces their bandwidth measurably,
if the decimation and interpolation filters do not have perfectly uniform phase
response, or if there is an unintended subsample time delay at any stage.

To measure the accuracy of our \gstreamer\ implemention of \lloid\ including all of
the above potential sources of \SNR\ loss, we conducted impulse response tests.  The
\gstreamer\ pipeline was presented with an input consisting of a unit impulse.  By
recording the outputs, we can effectively ``play back'' the templates.  These impulse
responses will be similar, but not identical, to the original, nominal templates.  By
taking the inner product between the impulses responses for each output 
channel with the corresponding nominal template, we can gauge exactly how much \SNR\
is lost due to the approximations in the \lloid\ algorithm and any of the technical
imperfections mentioned above.
